---
title: "Google General Tips and Tricks"
output: rmarkdown::html_vignette
author: "Teresa Engelbrecht, Marta Bofill Roig, Pavla Krotka"
vignette: >
  %\VignetteIndexEntry{Google General Tips and Tricks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# General hacks & shortcuts

## Search for exact request 

- Use quotes to search for your exact request, not just the words in any order

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504659057012736", hide_thread = TRUE)
```

- Use two periods within two numbers to search for ranges:
  E.g. Books 1990..2000

## Search specific kind or location

- Use `filetype:pdf` to find all PDFs related to your search request

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504679789453312", hide_thread = TRUE)
```

- Use `site:xxx` to search a specific site xxx

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504665956700162", hide_thread = TRUE)
```

- Add `@` in front of a word to search social media

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504686487752705", hide_thread = TRUE)
```

- Tune your image search to specific colour, size, copyright, time oder type

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504696164036608", hide_thread = TRUE)
```

- Use `-` to exclude words or phrases from the results

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504724878225410", hide_thread = TRUE)
```


## Comparison in searches

- Use `related:xxx` to find sites related to xxx

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504672751472641", hide_thread = T)
```

- Use `VS` to compare two or more things

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504702887464960", hide_thread = T)
```

- Use `~` in front of a word to find synonyms

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504729999552513", hide_thread = T)
```

- Use `|` (vertical bar) or `OR` to generalize searches. 

## Create Google Alert

- To get notified whenever a keyword is published on the web create a [Google Alert](https://www.google.com/alerts)

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504722055516160", hide_thread = T)
```



# For slower days

- Use Google search to do math

- Use Google for a reverse Image Search
  Upload an image file and find information on that image

- Use `[number]=language` to spell out numbers in specified language

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504709401300997", hide_thread = T)
```

- Play fun games in Google Search

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504715776565248", hide_thread = T)
```

- Use `*` in place of words you do not know

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Infinitians1/status/1546504737851248641", hide_thread = T)
```


# Reference

- [Twitter Thread](https://twitter.com/Infinitians1/status/1546504649624064000?t=hWHi699aZMOb9U7NGNDoOQ&s=08)