---
title: "R General Tips and Tricks"
output: rmarkdown::html_vignette
author: "Teresa Engelbrecht, Marta Bofill Roig, Pavla Krotka"
vignette: >
  %\VignetteIndexEntry{R General Tips and Tricks}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# General hacks & shortcuts

## Multi-line editing

- Use `alt` to mark multiple lines 


```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/EikoFried/status/1069646675814375425", widget_type = "video")
```

- Use `ctrl + alt_left + mouse_left` to spawn multiple cursors

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Chr_Koenig/status/1512352942443143172", widget_type = "video", hide_thread = T, plain = T)
```


## Commenting blocks


- Use `ctrl + Shift + c` to comment/uncomment an entire code block

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Chr_Koenig/status/1512352922587312133", widget_type = "video", hide_thread = T)
```


## Moving selections

- Use `alt_left + up/down` to move selections up and down

```{r, echo=FALSE}
tweetrmd::tweet_embed("https://twitter.com/Chr_Koenig/status/1512352957186125828", widget_type = "video", hide_thread = T)
```


# Useful resources

## Gereral

- [Cheatsheets](https://www.rstudio.com/resources/cheatsheets/)

- [CRAN Explorer](https://shiny.rstudio.com/gallery/cran-explorer.html) 

## Simulation of clinical trials

- [RCT Simulations Github Repository](https://github.com/aalthous/RCT-Simulations) 

## Parallel computing & Code optimisation

- [Quick Intro to Parallel Computing in R](https://nceas.github.io/oss-lessons/parallel-computing-in-r/parallel-computing-in-r.html)
- [Implementing Parallel Processing in R](https://www.r-bloggers.com/2017/08/implementing-parallel-processing-in-r/#:~:text=There%20are%20various%20packages%20in,subset%20to%20make%20a%20cluster)

- [Profvis - Interactive Visualizations for Profiling R Code](https://rstudio.github.io/profvis/)

## Twitter accounts 

- [One R Tip a Day](https://twitter.com/RLangTip)

- [Rstats](https://twitter.com/rstatstweet)

- [RStudio Tips](https://twitter.com/rstudiotips) 

- [RStudio](https://twitter.com/rstudio)
