---
title: "R Package Websites"
output: rmarkdown::html_vignette
author: "Marta Bofill Roig, Pavla Krotka"
vignette: >
  %\VignetteIndexEntry{R Package Websites}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Why should my package have a website?

- clear and structured way of presenting your package
- more user-friendly documentation of the package structure and its functions
- additional information and sites can be included via vignettes
- can be easily created using the `pkgdown` package


## How to create a website for an R package in 4 simple steps

1. Install development version from GitHub
```{r, eval=F}
devtools::install_github("MartaBofillRoig/IMS-software/ToyPackage", build = TRUE, force = TRUE)
```

2. Make sure your working directory is the package folder
```{r, eval=F}
filepath <- "C:/Users/pavla/Nextcloud/GitKraken/IMS-software/ToyPackage"
setwd(filepath)
```

3. Run once to configure your package to use pkgdown
```{r, eval=F}
usethis::use_pkgdown()
```

4. Run to build the website
```{r, eval=F}
pkgdown::build_site()
```

