---
title: "Software for Reproducible Research -- R Package Development"
author: "Marta Bofill Roig and Pavla Krotka"
date: "IMS-RETREAT 2022"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Why do I need to build my own package?

Packaging our functions in R packages. Why should I do it?

- is easily executable and shareable code
- makes reusable R functions
- includes documentation that describes how to use them 
<!-- - includes examples to illustrate their use -->
- makes reproducible R code 

## How to create an R package in 4 simple steps

1. Define the working directory
```{r, eval=F} 
filepath <- "C:/Users/pavla/Nextcloud/GitKraken/IMS-software/ToyPackage"
```

2. Create r package folder
```{r, eval=F} 
usethis::create_package()  
```

3. Copy in R folder the functions of the r package 
```{r, eval=F} 
setwd(filepath)
devtools::document()
devtools::load_all() 
```

4. Build and check the package
```{r, eval=F} 
devtools::build(pkg = filepath, path = NULL, binary = FALSE, manual = TRUE)
devtools::check_built(path = filepath, cran=TRUE, manual = TRUE)
devtools::build_manual(pkg = filepath, path = NULL)
```

